A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Well spotted Ciaran

\paragraph{\cref{McSplitAlg} in detail} The recursive procedure, $\FuncSty{expand}$, has
two parameters.  The parameter $\AlgVar{future}$ is a list of label classes,
each represented as a $\langle P, T \rangle$ pair as described above.  The
parameter $M$ is the current mapping of vertices.  On each call to
$\FuncSty{expand}$, the invariant holds that a $(v,w)$ pair may be added to $M$
if and only if $v$ and $w$ belong to the same label class in $M$ ?? shouldn't that be future?.

>>>>

\paragraph{\cref{McSplitAlg} in detail} The recursive procedure, $\FuncSty{expand}$, has
two parameters.  The parameter $\AlgVar{future}$ is a list of label classes,
each represented as a $\langle P, T \rangle$ pair as described above.  The
parameter $M$ is the current mapping of vertices.  On each call to
$\FuncSty{expand}$, the invariant holds that a $(v,w)$ pair may be added to $M$
if and only if $v$ and $w$ belong to the same label class in $\AlgVar{future}$.
